### 2017-02-13 section/3_redundancy.tex
shrink to 10 pages

\begin{figure}
  \centering
  \lstset{basicstyle=\ttfamily\fontsize{8}{8}\selectfont,
     morekeywords={+},keepspaces=true,numbers=left}
  \mbox{\lstinputlisting[mathescape,boxpos=t]{figures/Apache34464.c}}
  \caption{A cross-loop redundant bug in Apache (The \texttt{for} loop on line 7 
searches a string \texttt{source} for a target sub-string 
\texttt{target}. Since the outer loop on line 2 appends one 
character to \texttt{source} in every iteration (line 30), 
the \texttt{for} loop is always working on a similar 
\texttt{source} from its previous execution, with a lot of redundancy.) 
}
  \label{fig:Apache34464}
\end{figure}

@@

{\color{red}
\Tool suggests a fix strategy for each inefficient loop based on the
inefficiency category. Making this suggestion is straightforward for
most categories, and requires a small amount of extra
analysis occasionally. \Tool also
provides related information for carrying out the suggested fix strategy. 
}

\comment{
\Tool suggests a fix strategy for each inefficient loop 
and provides related information for carrying out that strategy.
This process is straightforward following our taxonomy discussion in 
Section \ref{sec:study}, as there are often only one or two natural fix 
strategies for each sub-category of root causes.
}

@@

When a loop is identified as \emph{redundant}, \Tool conducts
extra analysis to
decide whether batching or memoization should be used. 
For cross-iteration redundancy, \Tool suggests batching if the
redundancy is related to I/O operations and suggests memoization otherwise.
Specifically, when the only side effect of a loop is from I/O operations
and the same statement(s) is executed in every iteration, \Tool suggests
batching the specific I/O operations.
Otherwise, \Tool suggests memoization, and reports
input instructions that lead to redundant computation and redundancy rate.

>>>>

\begin{figure}
  \centering
  \lstset{basicstyle=\ttfamily\fontsize{7}{8}\selectfont,
     morekeywords={+},keepspaces=true,numbers=left}
  \mbox{\lstinputlisting[mathescape,boxpos=t]{figures/Apache34464.c}}
  \caption{A cross-loop redundant bug in Apache 
{\footnotesize{(The \texttt{for} loop on line 7 
searches a string \texttt{source} for a target sub-string 
\texttt{target}. Since the outer loop on line 2 appends one 
character to \texttt{source} in every iteration (line 30), 
the \texttt{for} loop is always working on a similar 
\texttt{source} from its previous execution, with a lot of redundancy.}}) 
}
  \label{fig:Apache34464}
\end{figure}

@@

\Tool suggests a fix strategy for each inefficient loop based on the
inefficiency category. Making this suggestion is straightforward for
most categories, and requires a small amount of extra
analysis occasionally. \Tool also
provides related information for carrying out the suggested fix strategy.

@@

When a loop is identified as \emph{redundant}, \Tool conducts
extra analysis to
decide whether batching or memoization should be used. 
For cross-iteration redundancy, \Tool suggests batching 
I/O operations.
when the only side effect of a loop is from I/O operations
and the same statement(s) is executed in every iteration.
Otherwise, \Tool suggests memoization, and reports
input instructions that lead to redundant computation and redundancy rate.

### 2017-02-13 section/5_exper.tex
shrink to 10 pages

\noindent\textbf{Benchmarks}
\Tool is a diagnosis tool that helps understand and fix 
already-manifested performance problems,
not a detection tool that help predict not-yet-manifested
problems. Consequently, our benchmarks are performance problems that have already
happened in real world, and we will reproduce them to evaluate \Tool.
For a thorough evaluation, we use
benchmarks from two different sources.

First, \emph{general} benchmark suite.
We evaluate \Tool on all bugs, 18 in total, that we can reproduce 
among the 45 bugs discussed in Section \ref{sec:eval_taxonomy}. 
These 18 bugs cover a wide variety of inefficiency root causes, as 
shown in the upper half of Table~\ref{tab:benchmarks}. 
We use the problem-triggering inputs reported by real-world
users in \Tool run-time analysis.
Among these 18, seven are extracted from Java/JavaScript
programs.
%, as \Tool currently only handles C/C++
%programs; one is extracted from a very old version of Mozilla that can no longer be
%compiled as it is.
%These 18 bugs include all the benchmarks used in the recent
%statistical performance debugging work~\cite{SongOOPSLA2014}.
%The extraction is conducted by XXX.
For these benchmarks, we did our best to keep all bug-related data structures
and caller/callee functions intact, and re-implement them in C++
following the original data and control flow. 
%Their
%bug-triggering inputs are produced based on the bug-triggering inputs in 
%the original bug reports.

Note that, we expect \Tool to also work for most, if not all, of 
the remaining 27 bugs listed in Table \ref{tab:root}.
However, these 27 bugs are too difficult to reproduce, as they 
depend on special hardware/software environment (e.g., Windows OS and 
.Net libraries) and cannot be easily extracted or reimplemented. 
For example, some bugs are related to GUI widgets, which are too complicated to 
re-implement. Some bugs' inefficient 
loops traverse big graphs, whose bug-triggering inputs
(i.e., the graphs) are difficult to figure out 
without reproducing the original bugs.

@@

\noindent\textbf{Evaluation settings}
Our evaluation uses existing statistical performance diagnosis
tool \cite{SongOOPSLA2014} to process a performance problem and identify 
one or a few suspicious loops for \Tool to analyze.
For all but four benchmarks, statistical debugging identifies the
real root-cause loop as the most suspicious loop. For the remaining four
benchmarks, which all come from Table \ref{tab:root},
the real root-cause loops are ranked number 2, 2, 4, and 10.
%Overall, we believe future tools can accurately identify the most one or a couple
%of suspicious loops.
%XXX (what can we say about Toddler benchmark set here?)

%\input section/tab_cover

We use 0.001 as the default \textit{resultful rate} threshold for identifying
0*1? 
%loops, 0.01 as the \textit{resultful rate} threshold for identifying 
and [0$|$1]* resultless loops; we use 
0.5 as the default \textit{redundancy rate} threshold for identifying redundant loops.
%, and 
%2 as the \textit{cross-iteration redundancy rate} (i.e., 
%the number of distinct iterations is less than half of the total iterations).
We use $1/100$ sampling rate for cross-loop redundancy analysis and 
$1/1000$ sampling rate for cross-iteration redundancy analysis
(there tend to be more loop iterations than loop instances).
All our diagnosis results require only \textbf{one} run under the 
problem-triggering input.
All our performance results are obtained by taking average of \textbf{ten} runs, 
with the variation among different runs always less than 5\%.

>>>>

\noindent\textbf{Benchmarks}
\Tool is a diagnosis tool that helps understand and fix 
already-manifested performance problems.
Consequently, our benchmarks are performance problems that have already
happened in real world.
For a thorough evaluation, we use
benchmarks from two different sources.

First, \emph{general} benchmark suite.
We evaluate \Tool on all bugs, 18 in total, that we can reproduce 
among the 45 bugs discussed in Section \ref{sec:eval_taxonomy}. 
These 18 bugs cover a wide variety of inefficiency root causes, as 
shown in the upper half of Table~\ref{tab:benchmarks}. 
We use the problem-triggering inputs reported by real-world
users in \Tool run-time analysis.
Among these 18, seven are extracted from Java/JavaScript
programs.
%, as \Tool currently only handles C/C++
%programs; one is extracted from a very old version of Mozilla that can no longer be
%compiled as it is.
%These 18 bugs include all the benchmarks used in the recent
%statistical performance debugging work~\cite{SongOOPSLA2014}.
%The extraction is conducted by XXX.
For these benchmarks, we did our best to keep all bug-related data structures
and caller/callee functions intact, and re-implement them in C++
following the original data and control flow. 
%Their
%bug-triggering inputs are produced based on the bug-triggering inputs in 
%the original bug reports.
We expect \Tool to also work for most of 
the remaining 27 bugs in Table \ref{tab:root}.
However, these 27 bugs are too difficult to reproduce, as they 
depend on special environment (e.g., Windows OS and 
.Net libraries) and cannot be easily extracted or reimplemented. 
For example, some bugs are related to GUI widgets and some 
require big complicated graphs to trigger.
%, which are too complicated to 
%re-implement. Some bugs' inefficient 
%loops traverse big graphs, whose bug-triggering inputs
%(i.e., the graphs) are difficult to figure out 
%without reproducing the original bugs.

@@

\noindent\textbf{Evaluation settings}
Our evaluation uses existing statistical performance diagnosis
tool \cite{SongOOPSLA2014} to process a performance problem and identify 
a few suspicious loops for \Tool to analyze.
For all but four benchmarks, statistical debugging identifies the
real root-cause loop as the most suspicious loop. For the remaining four,
which all come from Table \ref{tab:root},
the real root-cause loops are ranked number 2, 2, 4, and 10.
%Overall, we believe future tools can accurately identify the most one or a couple
%of suspicious loops.
%XXX (what can we say about Toddler benchmark set here?)
%\input section/tab_cover
We use 0.001 as the default \textit{resultful rate} threshold for identifying
0*1? 
%loops, 0.01 as the \textit{resultful rate} threshold for identifying 
and [0$|$1]* resultless loops; we use 
0.5 as the default \textit{redundancy rate} threshold for identifying redundant loops.
%, and 
%2 as the \textit{cross-iteration redundancy rate} (i.e., 
%the number of distinct iterations is less than half of the total iterations).
We use $1/100$ sampling rate for cross-loop redundancy analysis and 
$1/1000$ sampling rate for cross-iteration redundancy analysis
(there tend to be more loop iterations than loop instances).
All our diagnosis results require only \textbf{one} run under the 
problem-triggering input.
All our performance results are obtained by taking average of \textbf{ten} runs, 
with the variation among different runs always less than 5\%.

### 2017-02-13 section/evaltax.tex
shrink to 10 pages

\comment{
Previous work \cite{PerfBug,SongOOPSLA2014} studied the on-line bug
databases of five representative open-source software projects:
(1) Apache suite, including HTTPD web server written in C/C++,
TomCat server written in Java, and Ant build management tool in Java;
(2) Chromium Google Chrome browser in C/C++;
(3) GCC compiler suite in C/C++;
(4) Mozilla suite, including Firefox web browser and Thunderbird
Email client in C/C++ and JavaScript; 
(5) MySQL database server in C/C++.
Through a mix of random sampling and 
manual inspection, they 
found 65 performance problems that are perceived and reported by users. 
Among these 65 problems, 45 problems are related to inefficient loops and 
hence are the target of the study 
here.
}

>>>>

\comment{
Previous work \cite{PerfBug,SongOOPSLA2014} studied the on-line bug
databases of five representative open-source software projects:
(1) Apache suite, including HTTPD web server written in C/C++,
TomCat server written in Java, and Ant build management tool in Java;
(2) Chromium Google Chrome browser in C/C++;
(3) GCC compiler in C/C++;
(4) Mozilla web browser and
Email client in C/C++ and JavaScript; 
(5) MySQL database server in C/C++.
Through a mix of random sampling and 
manual inspection, they 
found 65 performance problems that are perceived and reported by users. 
Among these 65 problems, 45 are related to inefficient loops and 
hence are the target of the study 
here.
}
